Decentralized Data Marketplace to Enable Trusted Machine Economy

### 2019-08-30 paper.tex
Revise equations

\begin{document}
%
\title{Decentralized Data Marketplace to Enable Trusted Machine Economy}
%
\author{
%%% Fill in name here
\IEEEauthorblockN{Zan-Jun Wang\IEEEauthorrefmark{3}, Ching-Hua Lin\IEEEauthorrefmark{2}, Yang-Hao Yuan\IEEEauthorrefmark{4}, Ching-Chun (Jim) Huang\IEEEauthorrefmark{1}}\\

%%% Fill in school here
\IEEEauthorblockA{\IEEEauthorrefmark{1}\IEEEauthorrefmark{2}Department of Computer Science and Information Engineering National Cheng Kung University} \\
\IEEEauthorblockA{\IEEEauthorrefmark{3}Department of Computer Science and Information Engineering National Taiwan University} \\
\IEEEauthorblockA{\IEEEauthorrefmark{4}BiiLabs, Co., Ltd.} \\

@@

%%% Fill in email here
\IEEEauthorblockA{\IEEEauthorrefmark{1}jserv@ccns.ncku.edu.tw, \IEEEauthorrefmark{2}jkrvivian@gmail.com, \IEEEauthorrefmark{3}twzjwang@gmail.com, \IEEEauthorrefmark{4}yanghau@biilabs.io}
}

@@

The authors want to ensure the sustainability of decentralized data marketplace. The utility structure of IoT econimic system and game theory models are presented in the work of Dusit Niyato et al.\cite{UtilityStruct}. Game theory provides a mathematical solution to proof the existence of Nash Equilibrium in IoT economy. data marketplace organizers can apply numerical analysis on game theory, which would help them to find out their optimal pofit.

@@

In our game theory model there are two kinds of players. One is data provider, and the other one is data buyer. Data provider would receive subscription fee for buying data each time the data is transmitted to data buyer.
The data buyer will keep buying data from data povider, only when the data sold by the data provider with high enough accuracy, $P_r$. We deonte this accuracy threshold with $\xi$.
Once the accuracy is lower than $\xi$, the data buyers would consider this data provider as a low quality data provider, and reject to buy the data from this data provider.

\subsection{Participants Registration}
At the beginning, the registrar creates a Registration Contract (Figure \ref{fig:registration_contract}), which maintains all participants' information, including their DID (Decentralized Identifiers) Documents and public keys. Then some trustworthy brokers who pass procedures for conformity assessment are added to the decentralized data marketplace. Anyone who would like to sell or purchase data may register to become the data providers or consumers. The registrar has the authority to agree with applications.

@@

\subsection{Launching and Searching Products}
To sell the sensing data, a data provider has to launch a new product on the data marketplace in advance. The data provider determines a trusted broker and asks the broker to create a new MAM channel and Product Contract (Figure \ref{fig:product_contract}).

@@

\subsection{Refunding}
It is probable that the sensor is malfunctioning after the consumers pay the subscription fee. To protect consumers' right, the subscription fee are not transfered to the data provider until all data is generated and uploaded to the MAM channel. If the expected data is not available, consumers can ask for refunds. We assume that less than half of consumers in the Product Contract are irrational and malicious. Each consumer can vote for refunding at any time. If the ratio of consent votes of refunding is higher than the $threshold$ at $k$th piece of data, the subscription fee is proportionally transfered to the data provider, broker and every consumer. The subscription fee can be prorated as below:

\begin{equation}
F_{DataProvider}(k) = N price \frac{k-1}{M} (1-F_{b}) (1-F_{t})
\end{equation}

\begin{equation}
F_{Broker}(k) = N price \frac{k-1}{M} F_{b} (1-F_{t})
\end{equation}

\begin{equation}
F_{Consumer}(k) = price \frac{M-k+1}{M} (1-F_{t})
\end{equation}

@@

\subsection{Game Theory Evaluation}
\subsubsection{Repeated Game}
Repeated game consists of serveral repetitions of some stage games. In each stage game, the action player takes will effect the actions that players are going to take in the future stages. Repeated game can be illustrated with a decision tree and described their payoff with discounted sum of payoff. Discounted sum of payoff can capture the idea that what the players truly pursue is the sum of payoff in all stages and payoff in different stages may varify.

\subsubsection{Model Description}
We use a repeated game to express the scenario of our Data Marketplace. Figure.\ref{fig:decision_tree} shows the decision tree to depict the the repeated game we used. Each level in this decision tree represents each round of data transmission from data provider to data buyers, and the data buyers would pay subscription fee, $p_s$, each person. The sum of all the subscription fee pays to data provider is denoted as $P_s$.

Refund is a major issue in our research. However, we don't have to take refund as a factor in our repeated game, since in our decentralized data marketplace we use smart contract to store the subscription fee which will be paid to buy the future data. The subscription fee will be paid as data provider provides new data. In other words, data provide doesn't need to take any procedure to transer subscription fee from his/her own account to data buyers' account. For the same reason, data provider has no responsibility on the refunding processing fee charged by the smart contract as well.

\begin{figure} \centering \includegraphics[width=3.3in]{img/decision_tree.png} \caption{Decision Tree}
    \label{fig:decision_tree} \end{figure}
For every $n$ round, the data provider would cost $C_{maintain}$ to maintain or enhance the sensors that data provider owns. We call this as a maintain period. Moreover, the value of data and the cost of maintenance will decrease as time pass, so we introduce a discounted factor $\beta$ to depict this phenomena.

We have these following assumptions:
\begin{itemize}
\item  There is no any other data providers provide the same product in Data Marketplace. Therefore, we can consider each provider's behavior independently. That means this decision tree represent the behavior of only one data provider.
\item  More than 51\% of data buyers are among complete information exchange state. In other words, once one of them launches voting for stopping buying data and refunding, they would succeed in refund voting.
\item  One of the data buyers who has complete information exchange with other 51\% buyers has the ability to examine the data quality. If unacceptably low accuracy data are delivered to data buyers, this examiner will spread this information out.
\end{itemize}

Based on the description above, the discounted sum of payoff for our repeated game is 
\begin{equation} \label{payoff}
\sum_{i=0}^{m}{\beta^{in}\cdot [(\sum_{j=0}^{n} \beta^j \cdot P_s) - C_{maintain}]}
\end{equation}

\begin{itemize}
\item $P_s$ is the sum of subscription price (fee) for all subscriber.
\item $C_{maintain}$ is the cost of sensor maintenance in $n$ round.
\item $\beta$ is discounted factor.
\item $n$ is how many round for one maintenance period.
\item $m$ is how many maintenance periods have been experienced in this repeated game.
\end{itemize}

Al-Fagih et al. presented\cite{DataPrice} $P_s$ is a sigmoid function of $P_r$, and based on rule of thumb $C_{maintain}$ is about a exponential function of $P_r$. We can substitute $P_s$ and $C_{maintain}$ with $P_r$ into Eq. (\ref{payoff}), then we can find out the Nash Equilibrium of repeated game easily.

>>>>

\begin{document}
%
\title{Decentralized Data Marketplace to Enable Trusted Machine Economy}
%
\author{
%%% Fill in name here
\IEEEauthorblockN{Ching-Chun (Jim) Huang\IEEEauthorrefmark{1}, Ching-Hua Lin\IEEEauthorrefmark{2}, Zan-Jun Wang\IEEEauthorrefmark{3}}\\

%%% Fill in school here
\IEEEauthorblockA{\IEEEauthorrefmark{1}\IEEEauthorrefmark{2}Department of Computer Science and Information Engineering National Cheng Kung University} \\
\IEEEauthorblockA{\IEEEauthorrefmark{3}Department of Computer Science and Information Engineering National Taiwan University} \\

@@

%%% Fill in email here
\IEEEauthorblockA{\IEEEauthorrefmark{1}jserv@ccns.ncku.edu.tw, \IEEEauthorrefmark{2}jkrvivian@gmail.com, \IEEEauthorrefmark{3}twzjwang@gmail.com}
}

@@

@@

\subsection{Participants Registration}
At the beginning, the registrar creates a Registration Contract (Figure \ref{fig:registration_contract}), which maintains all participants' information, including their DID (Decentralized Identifiers) Documents and public keys. Only one Registration Contract is needed, and everyone can query the participants' public keys. Then some trustworthy brokers who pass procedures for conformity assessment are added to the decentralized data marketplace. Anyone who would like to sell or purchase data may register to become the data providers or consumers. The registrar has the authority to agree with applications. After that, their identities are available in the Registration Contract and launching and trading processes can be started.

@@

\subsection{Launching and Searching Products}
To sell the sensing data, a data provider has to launch a new product on the data marketplace in advance. The data provider determines a trusted broker and asks the broker to create a new MAM channel and Product Contract (Figure \ref{fig:product_contract}). Each product has a Product Contract to record the trading process.

@@

\subsection{Refunding}
It is probable that the sensor is malfunctioning after the consumers pay the subscription fee. To protect consumers' right, the subscription fee are not transfered to the data provider until all data is generated and uploaded to the MAM channel. If the expected data is not available, consumers can ask for refunds. We assume that less than half of consumers in the Product Contract are irrational and malicious. Each consumer can vote for refunding at any time. If the ratio of consent votes of refunding is higher than the $threshold$ at $i$th piece of data, the subscription fee is proportionally transfered to the data provider, broker and every consumer. The subscription fee can be prorated as below:

\begin{equation}
F_{DataProvider}(i) = N price \frac{i-1}{M} (1-F_{b}) (1-F_{t})
\end{equation}

\begin{equation}
F_{Broker}(i) = N price \frac{i-1}{M} F_{b} (1-F_{t})
\end{equation}

\begin{equation}
F_{Consumer}(i) = price \frac{M-i+1}{M} (1-F_{t})
\end{equation}

@@
